### 2014-11-13 tex/javalite.tex
Removed extra space on comma

A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. The only primitive type in Javalite is
Boolean. Classes have non-primitive fields , $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
methods, $(\cfgnt{M}\ ...)$.\footnote{Summary heaps are able to support non-primitive fields (see \secref{sec:eval}). They are omitted to focus and simplify the presentation.} Methods are limited to a single
parameter in our Javalite machine. Expressions, $\cfgnt{e}$,  
include statements, and they
 use '$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate comparison.
The dot-operator for field access is replaced by '$\cfgt{\$}$', and the dot-operator
for method invocation is replaced by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no explicit return
statement in Javalite; rather, the value of the last expression is
used as the return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap, $\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
We assume that only
type correct programs are given as input to the machine.

>>>>

A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. The only primitive type in Javalite is
Boolean. Classes have non-primitive fields, $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
methods, $(\cfgnt{M}\ ...)$.\footnote{Summary heaps are able to support non-primitive fields (see \secref{sec:eval}). They are omitted to focus and simplify the presentation.} Methods are limited to a single
parameter in our Javalite machine. Expressions, $\cfgnt{e}$,  
include statements, and they
 use '$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate comparison.
The dot-operator for field access is replaced by '$\cfgt{\$}$', and the dot-operator
for method invocation is replaced by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no explicit return
statement in Javalite; rather, the value of the last expression is
used as the return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap, $\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
We assume that only
type correct programs are given as input to the machine.
